Avoiding the Global Sort: \break A Faster Contour Tree Algorithm \footnote{The full updated version of this paper is available online \url{\si{http://web.engr.illinois.edu/\string~\si{raichel2}/\si{paint.pdf}}}}

### 2015-04-01 paint-contour-tree.tex

But this is only a worst-case bound. All previous algorithms begin by sorting (at least) the critical points, and
hence must pay $\Omega(t\log t)$ for all instances. Can we beat this sorting bound for certain instances,
and can we characterize which inputs are hard? Our main result gives an affirmative answer. First, we require a technical definition.

>>>>

But this is only a worst-case bound. All previous algorithms begin by sorting (at least) the critical points, and
% <<<<<<< HEAD
% hence must pay $\Omega(t\log t)$ for all instances. Can we beat this sorting bound for certain instances,
% and can we characterize which inputs are hard? Our main result gives an affirmative answer. First, we require a technical definition.
% =======
hence must pay $\Omega(t\log t)$ for all instances. Can one beat this sorting bound for some instances
and characterize what inputs are hard? Our main result gives an affirmative answer. 
% First, we require some technical definitions.
%>>>>>>> bbe1b0b1cd16827b201e5bfef1d03efbc4caa55f
